Uncertainty Quantification and Inference of Manning's Friction Coefficient using DART Buoys Data during \tohoku Tsunami

### 2014-02-02 friction_paper/cover.tex
Move first paper to new directory
This is to make it easy to start on the tohoku-okada-pc study

\end{Large}
\bigskip
\bigskip
Ihab Sraj$^1$, Kyle Mandli$^2$ \& Ibrahim Hoteit$^1$\\
\bigskip
$^1$Department of Physical Sciences and Engineering,
King Abdullah University for Science and Technology, Thuwal, Saudi Arabia \\
$^2$Department of Engineering, Austin, TX 
\end{center}

>>>>

\end{Large}
\bigskip
\bigskip
Ihab Sraj$^1$, Kyle Mandli$^2$, Ibrahim Hoteit$^1$, \& Clint Dawson$^2$\\
\bigskip
$^1$Department of Physical Sciences and Engineering,
King Abdullah University for Science and Technology, Thuwal, Saudi Arabia \\
$^2$Institute for Computational Engineering and Science\\
University of Texas at Austin\\
Austin, TX 
\end{center}

### 2014-02-02 friction_paper/intro.tex
Move first paper to new directory
This is to make it easy to start on the tohoku-okada-pc study

Previous work concerning uncertainty in tsunami modeling has been primarily been focused on constraining the likely earthquake source models (see
for example \cite{MacInnes:2013cr}).  A similar approach for landslide-generated
tsunami was presented in Sarri \emph{et al.}~\cite{Sarri2012}, by building a statistical surrogate
using an emulator. The implemented emulator was based on a Gaussian
process that requires using a combination of prior knowledge about the simulator
and appropriate choices of functions and parameters. Their work was presented as
a proof-of-concept case study where they only performed basic statistical and
sensitivity analysis.  Changes to the friction parameterization has been shown in 
the past to lead to significant changes in predicted inundation levels \cite{Myers:2001el, 
Jakeman:2010hk}, but these previous studies were limited in range and spatial variation of the values used in the parameterization.  
In a recent work, Mayo \emph{et al.}~\cite{Mayo:2014} reformulated a statistical data assimilation method
generally used in the estimation of model states to estimate the Manning's $n$
coefficient. They used a low-dimensional representation of
Manning's $n$ coefficients and recovered it by assimilating synthetic water elevation data
in a storm surge setting.

>>>>

Previous work concerning uncertainty in tsunami modeling has been primarily been focused on constraining the likely earthquake source models (see
for example \cite{MacInnes:2013cr}).  A similar approach for landslide-generated
tsunami was presented in Sarri \emph{et al.}~\cite{Sarri2012}, by building a statistical surrogate
using an emulator. The implemented emulator was based on a Gaussian
process that requires using a combination of prior knowledge about the simulator
and appropriate choices of functions and parameters. Their work was presented as
a proof-of-concept case study where they only performed basic statistical and
sensitivity analysis.  Changes to the friction parameterization has been shown in 
the past to lead to significant changes in predicted inundation levels \cite{Myers:2001el, 
Jakeman:2010hk}, but these previous studies were limited in range and spatial variation of the values used in the parameterization.  
In a recent work, Mayo \emph{et al.}~\cite{Mayo:2014} reformulated a statistical data assimilation method
generally used in the estimation of model states to estimate the Manning's $n$
coefficient. They used a low-dimensional representation of
Manning's $n$ coefficients and recovered it by assimilating synthetic water elevation data using tidal simulations.
